---
title: "Dog Jealousy- analysis Script"
author: "CV"
date: "February 14, 2021"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = TRUE)

rm(list=ls())


library(lme4)
library(MASS) 
library(ggthemes)
library(psych)
library(cowplot)
library(glmmTMB)
library(eeptools)
library(car)
library(ggsignif)
library(tidyverse)
library(summarytools)

source("./functions/diagnostic_fcns.r")
source("./functions/glmm_stability.r")
source("./functions/boot_glmm.r")
source("./functions/drop1_para.r")


```

## Load raw data
```{r loading data, include = FALSE}
agg.data <- read.csv(file="data/dog_jealousy_aggregated_data.csv")

view(dfSummary(agg.data))

hist(agg.data$blocking.sum)
hist(agg.data$non.off.manipulation.sum)
hist(agg.data$dom.beh.sum)
hist(agg.data$interaction.dog.sum)
hist(agg.data$first_approach_dog)
hist(agg.data$sniffing.dog.sum)
hist(agg.data$sniff.dog.anal.sum)
hist(agg.data$friendly_beh_humans.sum)


table(agg.data$condition, agg.data$blocking.presence)
table(agg.data$condition, agg.data$non.off.manipulation.presence)
table(agg.data$condition, agg.data$dom.beh.presence)
table(agg.data$condition, agg.data$friendly_beh_humans.presence)

```

## Centering variables for modeling
``` {r error=TRUE}
model.data <- agg.data %>% 
  mutate(z.age = as.numeric(scale(age, scale = T, center = T)),
         sex.c = as.numeric(scale(as.numeric(as.factor(sex)), scale = F, center = T)))

as.data.frame(model.data)
view(dfSummary(model.data))
```


## Blocking variable

```{r}
blocking.glm01 <- glm(blocking.presence ~ human * treatment + z.age + sex, 
             data = model.data, family = binomial)

drop1(blocking.glm01, test="Chisq")#likelihood ratio test
```

```{r}
blocking.glm02 <- glm(blocking.presence ~ human + treatment + z.age + sex, 
             data = model.data, family = binomial)

summary(blocking.glm02)

drop1(blocking.glm02, test="Chisq")#likelihood ratio test
```

#### full-null model comparison

```{r}
# null model
blocking.null <- glm(blocking.presence ~ z.age + sex, 
             data = model.data, family = binomial)

# comparison
anova(blocking.glm02, blocking.null, test="Chisq")
# --> sign. 0.03

```


#### check for collinearity in the previous model.

```{R echo=FALSE, error=FALSE, warning=FALSE}

col.blocking.glm <- lm(blocking.presence ~ human + treatment + z.age + sex, data = model.data)
vif(col.blocking.glm)
```



#### Model stability
```{r}
cbind(coef(blocking.glm02), coef(blocking.glm02)+t(apply(X=dfbeta(blocking.glm02), MARGIN=2, FUN=range)))
# min and max of model estimates
```

#### Confidence intervals
```{r}
cbind(orig=coefficients(blocking.glm02), confint(object=blocking.glm02))
```

### CI for the plot

```{r}
blocking.glm02.ci <- glm(blocking.presence ~ human + treatment + z.age + sex.c, 
             data = model.data, family = binomial)
##adding fitted values
fv=rep(NA, times=4)
fv[1]=coef(blocking.glm02.ci )["(Intercept)"]
fv[2]=sum(coef(blocking.glm02.ci)[c("(Intercept)", "treatmentP")])
fv[3]=sum(coef(blocking.glm02.ci)[c("(Intercept)", "humanS")])
fv[4]=sum(coef(blocking.glm02.ci)[c("(Intercept)", "treatmentP",
"humanS")])
fv=exp(fv)/(1+exp(fv))

to.plot <- model.data %>%
  group_by(human, treatment)%>%
  summarise(mean.blocking=mean(blocking.presence))%>%
  ungroup()

to.plot$z.age=0
to.plot$sex.c=0


ci.plot=predict.glm(object=blocking.glm02.ci, newdata=to.plot,type="link", se.fit=T)


ci.plot=data.frame(
lwr=ci.plot$fit-ci.plot$se.fit*
abs(qt(p=0.025, df=blocking.glm02.ci$df.residual)),
upr=ci.plot$fit+ci.plot$se.fit*
abs(qt(p=0.025, df=blocking.glm02.ci$df.residual))
)
ci.plot=exp(ci.plot)/(1+exp(ci.plot))

to.plot=(cbind(to.plot, fv, ci.plot))

```



### plotting

```{r}

blocking.plot.data <- agg.data %>%
  mutate(human = fct_recode(human, "Caregiver" = "C", "Stranger" = "S"), treatment=fct_recode(treatment, "Vet Check"="M", "Greeting"="P"))%>% #renaming of factor levels
  group_by(condition, human, treatment)%>%
  summarise(mean.blocking=mean(blocking.presence), sd.blocking=sd(blocking.presence),  median.blocking=median(blocking.presence),  se.blocking=sd(blocking.presence)/sqrt(length(blocking.presence)))

blocking.plot.data <- cbind(as.data.frame(blocking.plot.data), fv, ci.plot)

plot.blocking <- ggplot(
  data=blocking.plot.data, aes(x=human, y=mean.blocking, fill=treatment)) +
  geom_bar(stat="identity", alpha=0.5, position=position_dodge(width = 0.9))+
  geom_errorbar(aes(ymin=lwr, ymax=upr), width = 0.5,position=position_dodge(width = 0.9)) +
  geom_point(aes(y=fv), position=position_dodge(width = 0.9)) +
  geom_signif(comparisons = list(c("Caregiver", "Stranger")), 
              annotation=c("*"), y_position = 0.79)+
  scale_fill_manual(values=c("dodgerblue","darkorange"))+
  ylim(0,1)+
  theme_classic()+
  labs(x="Condition",y="Blocking")+
  theme(legend.title = element_blank(), legend.position = c(0.8, 0.9))+
    guides(fill = guide_legend(override.aes = list(shape = NA)))
 # theme(legend.position = "none")

plot.blocking

ggsave(plot.blocking, filename = "graphs/blocking_plot.png", width = 8, height = 6, scale = 0.65)
```


## Interaction with fake dog


```{r}
int.glm01 <- glm(interaction.dog.presence ~ human * treatment + z.age + sex, 
             data = model.data, family = binomial)

summary(int.glm01)

drop1(int.glm01, test="Chisq")#likelihood ratio test

```

```{r}
int.glm02 <- glm(interaction.dog.presence ~ human + treatment + z.age + sex, 
             data = model.data, family = binomial)

summary(int.glm02)

drop1(int.glm02, test="Chisq")#likelihood ratio test
```

#### full-null model comparison

```{r}
# null model
int.null <- glm(interaction.dog.presence ~ z.age + sex, 
             data = model.data, family = binomial)

# comparison
anova(int.glm02, int.null, test="Chisq")
# --> sign. 0.004

```

#### check for collinearity in the previous model.

```{R echo=FALSE, error=FALSE, warning=FALSE}

col.int.glm <- lm(interaction.dog.presence ~ human + treatment + z.age + sex, data = model.data)
vif(col.int.glm)
#no problem
```

#### Model stability
```{r}
cbind(coef(int.glm02),coef(int.glm02)+t(apply(X=dfbeta(int.glm02), MARGIN=2, FUN=range)))
```

#### Confidence intervals
```{r}
cbind(orig=coefficients(int.glm02), confint(object=int.glm02))
```

### CI for the plot

```{r}
int.glm02.ci <- glm(interaction.dog.presence ~ human + treatment + z.age + sex.c, 
             data = model.data, family = binomial)
##adding fitted values
fv=rep(NA, times=4)
fv[1]=coef(int.glm02.ci )["(Intercept)"]
fv[2]=sum(coef(int.glm02.ci)[c("(Intercept)", "treatmentP")])
fv[3]=sum(coef(int.glm02.ci)[c("(Intercept)", "humanS")])
fv[4]=sum(coef(int.glm02.ci)[c("(Intercept)", "treatmentP",
"humanS")])
fv=exp(fv)/(1+exp(fv))

to.plot <- model.data %>%
  group_by(human, treatment)%>%
  summarise(mean.int=mean(interaction.dog.presence))%>%
  ungroup()

to.plot$z.age=0
to.plot$sex.c=0


ci.plot=predict.glm(object=int.glm02.ci, newdata=to.plot,type="link", se.fit=T)


ci.plot=data.frame(
lwr=ci.plot$fit-ci.plot$se.fit*
abs(qt(p=0.025, df=int.glm02.ci$df.residual)),
upr=ci.plot$fit+ci.plot$se.fit*
abs(qt(p=0.025, df=int.glm02.ci$df.residual))
)
ci.plot=exp(ci.plot)/(1+exp(ci.plot))

to.plot=(cbind(to.plot, fv, ci.plot))

```



### plotting

```{r}

int.plot.data <- model.data %>%
  mutate(human = fct_recode(human, "Caregiver" = "C", "Stranger" = "S"), treatment=fct_recode(treatment, "Vet Check"="M", "Greeting"="P"))%>% #renaming of factor levels
  group_by(condition, human, treatment)%>%
  summarise(mean.int=mean(interaction.dog.presence), sd.int=sd(interaction.dog.presence),  median.int=median(interaction.dog.presence),  se.int=sd(interaction.dog.presence)/sqrt(length(interaction.dog.presence)))

int.plot.data <- cbind(as.data.frame(int.plot.data), fv, ci.plot)


plot.int <- ggplot(
  data=int.plot.data, aes(x=human, y=mean.int, fill=treatment)) +
  geom_bar(stat="identity", alpha=0.5, position=position_dodge(width = 0.9))+
  geom_errorbar(aes(ymin=lwr, ymax=upr), width = 0.5,position=position_dodge(width = 0.9)) +
  geom_point(aes(y=fv), position=position_dodge(width = 0.9)) +
  scale_fill_manual(values=c("dodgerblue","darkorange"))+
  geom_signif(comparisons = list(c("Caregiver", "Stranger")), 
              annotation=c("*"), y_position = 0.9)+
  geom_signif(y_position = c(0.8, 0.8), xmin = c(0.8, 1.8), xmax = c(1.2, 2.2),
    annotation = c("*", "*"))+
  #geom_signif(aes(xmin = xmin, xmax = xmax, y_position = y_position, annotations = signif), data=stat.test, manual = TRUE, tip_length = 0)+
  ylim(0,1)+
  theme_classic()+
  labs(x="Condition",y="Friendly interaction w. fake dog")+
  #theme(legend.title = element_blank(), legend.position = c(0.8, 0.9))+
  #guides(fill = guide_legend(override.aes = list(shape = NA)))+
  theme(legend.position = "none")
plot.int

ggsave(plot.int , filename = "graphs/int_plot.png", width = 8, height = 6, scale = 0.65) # not running yet due to new csv file
```


## Anal sniffing dog

```{r}
anal.sniff.glm01.poisson <- glm(sniff.dog.anal.sum ~ human * treatment + z.age + sex, 
             data = model.data, family = poisson)

overdisp.test(anal.sniff.glm01.poisson)

```

```{r}
anal.sniff.glm01.nb=glm.nb(sniff.dog.anal.sum ~ human * treatment + z.age + sex, data = model.data)
overdisp.test(anal.sniff.glm01.nb)
drop1(anal.sniff.glm01.nb, test="Chisq")
# interaction not significant
```


```{r}
anal.sniff.glm02.nb=glm.nb(sniff.dog.anal.sum ~ human + treatment + z.age + sex, data = model.data)

overdisp.test(anal.sniff.glm02.nb)

summary(anal.sniff.glm02.nb)

drop1(anal.sniff.glm02.nb, test="Chisq")#likelihood ratio test
```

#### full-null model comparison

```{r}
# null model
anal.sniff.null.nb=glm.nb(sniff.dog.anal.sum ~  z.age + sex, data = model.data)

# comparison
anova(anal.sniff.glm02.nb, anal.sniff.null.nb, test="Chisq") # anova not possible for 
```


#### check for collinearity in the previous model.

```{R echo=FALSE, error=FALSE, warning=FALSE}

col.anal.sniff.glm <- lm(sniff.dog.anal.sum ~ human + treatment + z.age + sex, data = model.data)
vif(col.anal.sniff.glm)
#no problem
```

#### Model stability
```{r}
cbind(coef(anal.sniff.glm02.nb),coef(anal.sniff.glm02.nb)+t(apply(X=dfbeta(anal.sniff.glm02.nb), MARGIN=2, FUN=range)))
```

#### Confidence intervals
```{r}
cbind(orig=coefficients(anal.sniff.glm02.nb), confint(object=anal.sniff.glm02.nb))
```

### CI for the plot

```{r}

anal.sniff.glm02.nb.ci=glm.nb(sniff.dog.anal.sum ~ human + treatment + z.age + sex.c, data = model.data)
##adding fitted values
fv=rep(NA, times=4)
fv[1]=coef(anal.sniff.glm02.nb.ci )["(Intercept)"]
fv[2]=sum(coef(anal.sniff.glm02.nb.ci)[c("(Intercept)", "treatmentP")])
fv[3]=sum(coef(anal.sniff.glm02.nb.ci)[c("(Intercept)", "humanS")])
fv[4]=sum(coef(anal.sniff.glm02.nb.ci)[c("(Intercept)", "treatmentP",
"humanS")])
fv=exp(fv)

to.plot <- model.data %>%
  group_by(human, treatment)%>%
  summarise(mean.int=mean(sniff.dog.anal.sum))%>%
  ungroup()

to.plot$z.age=0
to.plot$sex.c=0


ci.plot=predict.glm(object=anal.sniff.glm02.nb.ci, newdata=to.plot,type="link", se.fit=T)


ci.plot=data.frame(
lwr=ci.plot$fit-ci.plot$se.fit*
abs(qt(p=0.025, df=anal.sniff.glm02.nb.ci$df.residual)),
upr=ci.plot$fit+ci.plot$se.fit*
abs(qt(p=0.025, df=anal.sniff.glm02.nb.ci$df.residual))
)
ci.plot=exp(ci.plot)

to.plot=(cbind(to.plot, fv, ci.plot))

```


### plotting

```{r}

anal.sniff.plot.data <- model.data %>%
  mutate(human = fct_recode(human, "Caregiver" = "C", "Stranger" = "S"), treatment=fct_recode(treatment, "Vet Check"="M", "Greeting"="P"))%>% #renaming of factor levels
  group_by(condition, human, treatment)%>%
  summarise(mean.sniff=mean(sniff.dog.anal.sum), sd.sniff=sd(sniff.dog.anal.sum),  median.sniff=median(sniff.dog.anal.sum),  se.sniff=sd(sniff.dog.anal.sum)/sqrt(length(sniff.dog.anal.sum)))

anal.sniff.plot.data <- cbind(as.data.frame(anal.sniff.plot.data), fv, ci.plot)

plot.anal.sniff <- ggplot(
  data=anal.sniff.plot.data, aes(x=human, y=mean.sniff, fill=treatment)) +
  geom_bar(stat="identity", alpha=0.5, position=position_dodge(width = 0.9))+
  geom_errorbar(aes(ymin=lwr, ymax=upr), width = 0.5,position=position_dodge(width = 0.9)) +
  geom_point(aes(y=fv), position=position_dodge(width = 0.9)) +
  scale_fill_manual(values=c("dodgerblue","darkorange"))+
  geom_signif(comparisons = list(c("Caregiver", "Stranger")), 
              annotation=c("*"), y_position = 4.5)+
  #geom_signif(aes(xmin = xmin, xmax = xmax, y_position = y_position, annotations = signif), data=stat.test, manual = TRUE, tip_length = 0)+
   ylim(0,5)+
   theme_classic()+
  labs(x="Condition",y="Sniffing of fake dog (count)")+
  theme(legend.position = "none")
plot.anal.sniff

ggsave(plot.anal.sniff , filename = "graphs/anal_sniffing_plot.png", width = 8, height = 6, scale = 0.65) 
```
## First approach of fake dog

```{r}
approach.model.data <- model.data %>% 
  filter(!is.na(first_approach_dog))%>%
  mutate(z.age = as.numeric(scale(age, scale = T, center = T)),
         sex.c = as.numeric(scale(as.numeric(as.factor(sex)), scale = F, center = T)))

approach.glm01 <- glm(first_approach_dog ~ human * treatment + z.age + sex, 
             data = approach.model.data, family = binomial)

summary(approach.glm01)

drop1(approach.glm01, test="Chisq")#likelihood ratio test

```

```{r}
approach.glm02 <- glm(first_approach_dog ~ human + treatment + z.age + sex, 
             data = approach.model.data, family = binomial)

summary(approach.glm02)

drop1(approach.glm02, test="Chisq")#likelihood ratio test
```

#### full-null model comparison

```{r}
# null model
approach.null <- glm(first_approach_dog ~ z.age + sex, 
             data = model.data, family = binomial)

# comparison
anova(approach.glm02, approach.null, test="Chisq")
# --> sign. 0.017

```

#### check for collinearity in the previous model.

```{R echo=FALSE, error=FALSE, warning=FALSE}

col.approach.glm <- lm(first_approach_dog ~ human + treatment + z.age + sex, data = model.data)
vif(col.approach.glm)
#no problem
```

#### Model stability
```{r}
cbind(coef(approach.glm02),coef(approach.glm02)+t(apply(X=dfbeta(approach.glm02), MARGIN=2, FUN=range)))
```

#### Confidence intervals
```{r}
cbind(orig=coefficients(approach.glm02), confint(object=approach.glm02))
```

### CI for the plot

```{r}
approach.glm02.ci <- glm(first_approach_dog ~ human + treatment + z.age + sex.c, 
             data = model.data, family = binomial)
##adding fitted values
fv=rep(NA, times=4)
fv[1]=coef(approach.glm02.ci )["(Intercept)"]
fv[2]=sum(coef(approach.glm02.ci)[c("(Intercept)", "treatmentP")])
fv[3]=sum(coef(approach.glm02.ci)[c("(Intercept)", "humanS")])
fv[4]=sum(coef(approach.glm02.ci)[c("(Intercept)", "treatmentP",
"humanS")])
fv=exp(fv)/(1+exp(fv))

to.plot <- model.data %>%
  group_by(human, treatment)%>%
  summarise(mean.approach=mean(first_approach_dog))%>%
  ungroup()

to.plot$z.age=0
to.plot$sex.c=0


ci.plot=predict.glm(object=approach.glm02.ci, newdata=to.plot,type="link", se.fit=T)


ci.plot=data.frame(
lwr=ci.plot$fit-ci.plot$se.fit*
abs(qt(p=0.025, df=approach.glm02.ci$df.residual)),
upr=ci.plot$fit+ci.plot$se.fit*
abs(qt(p=0.025, df=approach.glm02.ci$df.residual))
)
ci.plot=exp(ci.plot)/(1+exp(ci.plot))

to.plot=(cbind(to.plot, fv, ci.plot))

```



### plotting

```{r}

approach.plot.data <- model.data %>%
  mutate(human = fct_recode(human, "Caregiver" = "C", "Stranger" = "S"), treatment=fct_recode(treatment, "Vet Check"="M", "Greeting"="P"))%>% #renaming of factor levels
  group_by(condition, human, treatment)%>%
  summarise(mean.approach=mean(first_approach_dog, na.rm=TRUE), sd.approach=sd(first_approach_dog),  median.approach=median(first_approach_dog),  se.approach=sd(first_approach_dog)/sqrt(length(first_approach_dog)))

approach.plot.data <- cbind(as.data.frame(approach.plot.data), fv, ci.plot)

plot.approach <- ggplot(
  data=approach.plot.data, aes(x=human, y=mean.approach, fill=treatment)) +
  geom_bar(stat="identity", alpha=0.5, position=position_dodge(width = 0.9))+
  geom_errorbar(aes(ymin=lwr, ymax=upr), width = 0.5,position=position_dodge(width = 0.9)) +
  geom_point(aes(y=fv), position=position_dodge(width = 0.9)) +
  scale_fill_manual(values=c("dodgerblue","darkorange"))+
  #geom_signif(aes(xmin = xmin, xmax = xmax, y_position = y_position, annotations = signif), data=stat.test, manual = TRUE, tip_length = 0)+
  ylim(0,1)+
  theme_classic()+
  labs(x="Condition",y="First approach of fake dog")+
  theme(legend.position = "none")+
    geom_signif(comparisons = list(c("Caregiver", "Stranger")), 
              annotation=c("*"), y_position = 0.98)
plot.approach

ggsave(plot.approach , filename = "graphs/approach_plot.png", width = 8, height = 6, scale = 0.65) # not running yet due to new csv file
```

## Friendly behaviors toward humans
```{r}
fb.humans.glm01 <- glm(friendly_beh_humans.presence ~ human * treatment + z.age + sex, 
             data = model.data, family = binomial)

drop1(fb.humans.glm01, test="Chisq")#likelihood ratio test

```

```{r}
fb.humans.glm02 <- glm(friendly_beh_humans.presence ~ human + treatment + z.age + sex, 
             data = model.data, family = binomial)

summary(fb.humans.glm02)

drop1(fb.humans.glm02, test="Chisq")#likelihood ratio test
```

#### full-null model comparison

```{r}
# null model
fb.humans.null <- glm(friendly_beh_humans.presence ~ z.age + sex, 
             data = model.data, family = binomial)

# comparison
anova(fb.humans.glm02, fb.humans.null, test="Chisq")

```

#### check for collinearity in the previous model.

```{R echo=FALSE, error=FALSE, warning=FALSE}

col.fb.humans.glm <- lm(friendly_beh_humans.presence ~ human + treatment + z.age + sex, data = model.data)
vif(col.fb.humans.glm)
#no problem
```

#### Model stability
```{r}
cbind(coef(fb.humans.glm02),coef(fb.humans.glm02)+t(apply(X=dfbeta(fb.humans.glm02), MARGIN=2, FUN=range)))
```

#### Confidence intervals
```{r}
cbind(orig=coefficients(fb.humans.glm02), confint(object=fb.humans.glm02))
```

### CI for the plot

```{r}
fb.humans.glm02.ci <- glm(friendly_beh_humans.presence ~ human + treatment + z.age + sex.c, 
             data = model.data, family = binomial)
##adding fitted values
fv=rep(NA, times=4)
fv[1]=coef(fb.humans.glm02.ci )["(Intercept)"]
fv[2]=sum(coef(fb.humans.glm02.ci)[c("(Intercept)", "treatmentP")])
fv[3]=sum(coef(fb.humans.glm02.ci)[c("(Intercept)", "humanS")])
fv[4]=sum(coef(fb.humans.glm02.ci)[c("(Intercept)", "treatmentP",
"humanS")])
fv=exp(fv)/(1+exp(fv))

to.plot <- model.data %>%
  group_by(human, treatment)%>%
  summarise(mean.fb_humans=mean(friendly_beh_humans.presence))%>%
  ungroup()

to.plot$z.age=0
to.plot$sex.c=0


ci.plot=predict.glm(object=fb.humans.glm02.ci, newdata=to.plot,type="link", se.fit=T)


ci.plot=data.frame(
lwr=ci.plot$fit-ci.plot$se.fit*
abs(qt(p=0.025, df=fb.humans.glm02.ci$df.residual)),
upr=ci.plot$fit+ci.plot$se.fit*
abs(qt(p=0.025, df=fb.humans.glm02.ci$df.residual))
)
ci.plot=exp(ci.plot)/(1+exp(ci.plot))

to.plot=(cbind(to.plot, fv, ci.plot))

```
### plotting

```{r}

fb.humans.plot.data <- model.data %>%
  mutate(human = fct_recode(human, "Caregiver" = "C", "Stranger" = "S"), treatment=fct_recode(treatment, "Vet Check"="M", "Greeting"="P"))%>% #renaming of factor levels
  group_by(condition, human, treatment)%>%
  summarise(mean.fb_humans=mean(friendly_beh_humans.presence, na.rm=TRUE), sd.fb_humans=sd(friendly_beh_humans.presence),  median.fb_humans=median(friendly_beh_humans.presence),  se.fb_humans=sd(friendly_beh_humans.presence)/sqrt(length(friendly_beh_humans.presence)))

fb.humans.plot.data <- cbind(as.data.frame(fb.humans.plot.data), fv, ci.plot)

plot.fb_humans <- ggplot(
  data=fb.humans.plot.data, aes(x=human, y=mean.fb_humans, fill=treatment)) +
  geom_bar(stat="identity", alpha=0.5, position=position_dodge(width = 0.9))+
  geom_errorbar(aes(ymin=lwr, ymax=upr), width = 0.5,position=position_dodge(width = 0.9)) +
  geom_point(aes(y=fv), position=position_dodge(width = 0.9)) +
  scale_fill_manual(values=c("dodgerblue","darkorange"))+
  #geom_signif(aes(xmin = xmin, xmax = xmax, y_position = y_position, annotations = signif), data=stat.test, manual = TRUE, tip_length = 0)+
  ylim(0,1)+
  theme_classic()+
  labs(x="Condition",y="Friendly interaction w. human")+
  theme(legend.position = "none")
    #geom_signif(comparisons = list(c("Caregiver", "Stranger")), annotation=c("p=0.056"), y_position = 0.98)
plot.fb_humans

ggsave(plot.fb_humans , filename = "graphs/fb_humans_plot.png", width = 8, height = 6, scale = 0.65) 
```

### combining plots
```{r}
plot.legend <- ggplot(
  data=approach.plot.data, aes(x=human, y=mean.approach, fill=treatment)) +
  geom_bar(stat="identity", alpha=0.5, position=position_dodge(width = 0.9))+
    scale_fill_manual(values=c("dodgerblue","darkorange"))+
    theme(legend.position = "top", legend.title = element_blank())
plot.legend

p.leg <- get_legend(plot.legend)

```

## behavioral categories: reaction phase
```{r fig.width=5, fig.height=4}
attitude.data<-read.csv(file = "data/dog_jealousy_attitude_reaction_phase_agg_data.csv")%>%
  mutate(treatment=fct_recode(treatment, "Vet Check"="M", "Greeting"="P"), attitude=as.factor(attitude))

attitude.data$attitude=factor(attitude.data$attitude,
levels=levels(attitude.data$attitude)[c(1, 4, 2, 3, 5)])
levels(attitude.data$attitude)

attitude.plot.react<- ggplot(data=attitude.data, aes(x=attitude, y=..prop.., group=1))+
  geom_histogram(stat="count")+
  theme_classic()+
  ylab("Proportion of dogs")+xlab("Attitude")+
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())

attitude.plot.react

ggsave(attitude.plot.react, filename = "graphs/attitude_plot_reaction_phase.png", width=6, height=5, scale=0.7)
```

### relation between behavioral categories and blocking

```{r}
attitude.data_blocking <- attitude.data%>%
  select(subject, attitude)%>%
  full_join(model.data)%>%
  mutate(blocking.presence = fct_recode(as.factor(blocking.presence), "No Blocking" = "0", "Blocking" = "1"))

attitude.data_blocking$blocking.presence<- relevel(attitude.data_blocking$blocking.presence, ref = "Blocking")
  

ctab<-table(attitude.data_blocking$attitude, attitude.data_blocking$blocking.presence)

fisher.test(ctab)
```


```{r}
attitude.plot.react.blocking<-ggplot(attitude.data_blocking) +
  aes(x = attitude,  fill=as.factor(blocking.presence))+
  geom_bar() +
  ylab("Number of dogs")+xlab("Attitude")+
  scale_fill_brewer(palette="Pastel1")+
  theme_classic()+
  theme(legend.title = element_blank(), legend.position = c(0.8, 0.9))

attitude.plot.react.blocking

```



```{r}

pg<-plot_grid(plot.approach,plot.int, plot.blocking, plot.anal.sniff , plot.fb_humans, attitude.plot.react.blocking, ncol=3, labels = c("A", "B", "C", "D", "E", "F"))
pg
#pg.leg<-plot_grid(p.leg, pg, rel_heights = c(0.1, 1), ncol=1)
#pg.leg
ggsave(pg, filename = "graphs/jealousy_all_reaction_phase_DVs.pdf", width = 16, height = 11, scale=0.6)

```

